NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-11-30 ms_nihao_budget.tex
fix a problem on afflication

\author[Wang et al.]{Liang Wang$^{1,3,4}$\thanks{wangliang@pmo.ac.cn}, Aaron A. Dutton$^{2,3}$,
  Gregory S. Stinson$^3$, Andrea V. Macci\`o$^{2,3}$, 
\newauthor{Thales Gutcke$^3$, Xi Kang$^1$}\\
$^1$Purple Mountain Observatory, the Partner Group of MPI f\"ur Astronomie, 2 West Beijing Road, Nanjing 210008, China\\
$^2$New York University Abu Dhabi, PO Box 129188, Abu Dhabi, UAE\\
$^3$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany\\
$^4$International Centre for Radio Astronomy Research (ICRAR)
, M468, University of Western Australia, 35 Stirling Hwy, Cr
awley, WA 6009, Australia}
\begin{document}

>>>>

\author[Wang et al.]{Liang Wang$^{1,3,4}$\thanks{wangliang@pmo.ac.cn}, Aaron A. Dutton$^{2,3}$,
  Gregory S. Stinson$^3$, Andrea V. Macci\`o$^{2,3}$, 
\newauthor{Thales Gutcke$^3$, Xi Kang$^1$}\\
$^1$Purple Mountain Observatory, the Partner Group of MPI f\"ur Astronomie, 2 West Beijing Road, Nanjing 210008, China\\
$^2$New York University Abu Dhabi, PO Box 129188, Abu Dhabi, UAE\\
$^3$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany\\
$^4$International Centre for Radio Astronomy Research (ICRAR)
, M468, University of Western Australia, 35 Stirling Hwy, \\
Crawley, WA 6009, Australia}
\begin{document}
